### 2019-02-21 sections/intuition.tex
fix breakfast, remove abstract examples

% \begin{TASK}
%   let makeBreakfast : Task Drink -> Task Food -> Task Unit =
%     \makeDrink . \makeFood . makeDrink <&> makeFood >>? \<<d, f>>. eat d f
%   let main : Task Unit =
%     makeBreakfast (makeTea <?> makeCoffee) makeEgg
% \end{TASK}

\begin{TASK}
  let makeBreakfast : Task Drink -> Task Food -> Task <<Drink,Food>> =
    \makeDrink . \makeFood . makeDrink <&> makeFood
  let main : Task Unit =
    (makeBreakfast (makeTea <?> makeCoffee) makeEgg) >>? \<<d, f>>. eat d f
\end{TASK}

% \begin{TASK}
%   let makeBreakfast : Task Drink -> Task Food -> Task Breakfast =
%     \makeDrink . \makeFood . makeDrink <&> makeFood
%   let main : Task Unit =
%     (makeBreakfast (makeTea <?> makeCoffee) makeEgg) >>? \breakfast. eat breakfast
% \end{TASK}

@@

\Cref{exm:breakfast} demonstrates how tasks can be parameterized by other tasks: makeBreakfast is a collaboration pattern that always works the same way, regardless of which food and drink are being prepared.

@@

>>>>

\lstset{emph={makeDrink,makeFood}}

% \begin{TASK}
%   let makeBreakfast : Task Drink -> Task Food -> Task Unit =
%     \makeDrink. \makeFood. makeDrink <&> makeFood >>? \<<d, f>>. eat d f
%   let main : Task Unit =
%     makeBreakfast (makeTea <?> makeCoffee) makeEgg
% \end{TASK}

\begin{TASK}
  let makeBreakfast : Task Drink -> Task Food -> Task <<Drink,Food>> =
    \makeDrink. \makeFood. makeDrink <&> makeFood in
  makeBreakfast (makeTea <?> makeCoffee) makeEgg >>? haveBreakfast
\end{TASK}

% \begin{TASK}
%   let makeBreakfast : Task Drink -> Task Food -> Task Breakfast =
%     \makeDrink. \makeFood. makeDrink <&> makeFood
%   let main : Task Unit =
%     makeBreakfast (makeTea <?> makeCoffee) makeEgg >>? \breakfast. eat breakfast
% \end{TASK}

@@

\Cref{exm:breakfast} demonstrates how tasks can be parameterised by other tasks: \TS{makeBreakfast} is a collaboration pattern that always works the same way, regardless of which food and drink are being prepared.

@@

% \lstset{emph={text}}
% \begin{example}[Abstract submission]
% \label{exm:abstract}
%
% The task of writing an abstract for a conference is never done.
% Let \TS{abstract} be a reference to a string.
%
% % \begin{TASK}
% %   let submit : String -> Task Unit =
% %     \text. delay 30 (sendTo "icfp19@sigplan.org" text)
% %   let write : Task Unit =
% %     edit "Abstract: ..." >>= \abstract. if 500 <= words abstract <= 700 then submit abstract else fail
% % \end{TASK}
%
% \begin{TASK}
%   let submit : Ref String -> Task String = \text. sendTo "icfp19@sigplan.org" text in
%   update abstract <|> delay 30 (submit abstract)
% \end{TASK}
%
% The \TS{delay} task is specified in Example~\ref{exm:delay} in Section~\ref{sec:language}.
%
% \end{example}
